\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-24 lang-design.tex
Adding comments in first few sections.

A key observation is that although late binding
prevents \emph{definitional equality} on \lsti{subst}, it does not
affect \emph{propositional equality}.
That is, \lsti{\forall x t, subst tm_unit x t = tm_unit},
as a proposition (\lsti{Prop}), should still hold.
After all, how \lsti{subst} is defined on \lsti{tm_unit} does not vary
from a base family to a derived family.
%
Based on this insight, our plugin automatically generates
propositional equalities for each recursive function defined with \lsti{FRecursion},
making them available as axioms for use by the rest of the current family.
The plugin also provides a tactic \lsti{fsimpl} that enables, for instance,
simplifying \lsti{subst tm_unit x t'} to \lsti{tm_unit}.
Under the hood, \lsti{fsimpl} works by rewriting using the postulated
propositional equalities.

Note that the definitional equality on \lsti{subst} is available
outside those families that contain "subst".
Within those families, the meaning of \lsti{subst} is late bound, so only
propositional equality is available.
In contrast, outside those families, \lsti{subst} is always referenced
by specifying a family that contains it,
such as \lsti{STLC.subst} or \lsti{STLCFix.subst}.
As far as the type checker is concerned, \lsti{tm_unit} and
\lsti{STLCFix.subst tm_unit x t'} are the same thing---the type checker
equates them definitionally by unfolding \lsti{STLCFix.subst} and
performing normalization.

>>>>

A key observation is that although late binding
prevents \emph{definitional equality} on \lsti{subst}, it does not
affect \emph{propositional equality}.
That is, \lsti{\forall x t, subst tm_unit x t = tm_unit},
as a proposition (\lsti{Prop}), should still hold.
After all, how \lsti{subst} is defined on \lsti{tm_unit} does not vary
from a base family to a derived family.\EDJ{I think the reviewer might ask : what if the subst late-bound tm_unit case/why the subst cases cannot be late-bound? it not necessary return tm_unit in those case. 
\\ What the plugin generates is actually subst tm_unit x t = subst.tm_unit. In other words, it points back to the handler instead of the concrete constructor. That is one of the advantage of looking FRecursion as a family.}
%
Based on this insight, our plugin automatically generates
propositional equalities for each recursive function defined with \lsti{FRecursion},
making them available as axioms for use by the rest of the current family.
The plugin also provides a tactic \lsti{fsimpl} that enables, for instance,
simplifying \lsti{subst tm_unit x t'} to \lsti{tm_unit}.
Under the hood, \lsti{fsimpl} works by rewriting using the postulated
propositional equalities.

Note that the definitional equality on \lsti{subst} is available
outside those families that contain "subst".
Within those families, the meaning of \lsti{subst} is late bound, so only
propositional equality is available.
In contrast, outside those families, \lsti{subst} is always referenced
by specifying a family that contains it, \EDJ{I think the reviewer without background of Family Polymorphism will be confused at this paragraph. i.e. Why inside family it is late-bound but not outside? }
such as \lsti{STLC.subst} or \lsti{STLCFix.subst}.
As far as the type checker is concerned, \lsti{tm_unit} and
\lsti{STLCFix.subst tm_unit x t'} are the same thing---the type checker
equates them definitionally by unfolding \lsti{STLCFix.subst} and
performing normalization.
